Bias Analysis

### 2023-11-01 archive/L1_NorthAndes_plants_BIEN_traits.Rmd

# Configure BIEN trait data to Darwin Core Standards
```{r}
# darwinizing a dataset
config <- read.csv(file.path(output_path,"configuration table.csv"))

>>>>

# Configure BIEN trait data to Darwin Core Standards
```{r}
# darwinizing a dataset
config <- read.csv(file.path(output_path,"Ecuador_plant_BIEN_trait_ConfigurationTable.csv"))

### 2023-11-01 code/L1/L1_F1_TropicalAndes_frugivores_GBIF.Rmd

```{r}
table(TropicalAndes_GBIF_frugivore_occ_cleaned$year)
```

```{r}
# remove records from before second world war
TropicalAndes_GBIF_frugivore_occ_cleaned <- TropicalAndes_GBIF_frugivore_occ_cleaned %>%
  filter(year > 1945) 
```

@@

```{r}
print("The number of records is")
nrow(TropicalAndes_GBIF_frugivore_occ_cleaned)
print("The number of species is")
length(unique(TropicalAndes_GBIF_frugivore_occ_cleaned$species))
print("The number of families is")
length(unique(TropicalAndes_GBIF_frugivore_occ_cleaned$family))
```

>>>>

@@

```{r}
print("The number of records is")
nrow(TropicalAndes_GBIF_frugivore_occ_cleaned)
print("The number of species is")
length(unique(TropicalAndes_GBIF_frugivore_occ_cleaned$species))
print("The number of genera is" )
length(unique(TropicalAndes_GBIF_frugivore_occ_cleaned$genus))
print("The number of families is")
length(unique(TropicalAndes_GBIF_frugivore_occ_cleaned$family))
```

### 2023-11-01 code/L1/L1_F3_TropicalAndes_frug_occ.Rmd

---
title: "TITLE"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script subsets frugivore occurrence data to species with complete trait coverage."
data input: "ADD"
data output: "ADD"
date: "2023-10-04"
output: html_document
---

# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
```

# Load required packages
```{r}

```

>>>>

---
title: "Frugivore occurrence subset by species with complete trait records"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script subsets frugivore occurrence data to species with complete trait coverage."
data input: "ADD"
data output: "ADD"
date: "2023-10-04"
output: html_document
---

# Set file paths
```{r}
data_path_L0<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
data_path_L1<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
```

# Load required packages
```{r}
library(dplyr)
#run if not installed remotes::install_github("FRBCesab/funbiogeo")
library(funbiogeo)
```

# Read in data
```{r}
Frugivoria_subset <- read.csv(file.path(data_path_L1, file = "TropicalAndes_Frugivoria_traits_subset.csv"))
frugivore_occ <- read.csv(file.path(data_path_L1, file = "TropicalAndes_GBIF_frugivore_occ_cleaned.csv"))
```

# Check trait coverage
```{r}
summary(Frugivoria_subset)
```
```{r}
fb_plot_number_species_by_trait(Frugivoria_subset)
```
```{r}
Frugivoria_complete <- fb_filter_species_by_trait_coverage(Frugivoria_subset, threshold_traits_proportion =  1)
```

```{r}
summary(Frugivoria_complete)
```

```{r}
fb_plot_number_species_by_trait(Frugivoria_complete)
```

# Create list of species with complete trait records
```{r}
frugivoria_species <- unique(Frugivoria_complete$IUCN_species_name)
```

# Subset frugivore occurrence data by species list
```{r}
frugivore_occ_subset <- frugivore_occ %>%
  filter(species %in% frugivoria_species)
```

# Summary
```{r}
glimpse(frugivore_occ_subset)
```

```{r}
source("~/GitHub/neotropical_plants/code/L0/data_summary.R")
```

```{r}
data_summary(frugivore_occ_subset, frugivore_occ_subset$species, frugivore_occ_subset$genus, frugivore_occ_subset$family)
```

# Write data to csv
```{r}
write.csv(frugivor_occ_subset, file.path(output_path,"TropicalAndes_GBIF_frugivore_occ_cleaned_subset.csv"))
```

### 2023-11-01 code/L2/L2_3_TropicalAndes_divRelationships.Rmd

---
title: "Combining taxonomic and functional diversity for plants and frugivores at various spatial grains"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script combines taxonomic and functional diversity per cell for various spatial grains for plants and frugivores."
data input: "ADD"
data output: "ADD"
date: "2023-10-04"
output: html_document
---

>>>>

---
title: "Diversity relationships for plants and frugivores"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script compares taxonomic and functional diversity relationships for plants and frugivores for various spatial grains and combined diversity for each grain."
data input: "ADD"
data output: "ADD"
date: "2023-10-04"
output: html_document
---

### 2023-11-01 code/L2/L2_TropicalAndes_data_bias.Rmd

---
title: "Plant-frugivore trait alignment"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script looks at pairs of traits between plants and frugivores to test alignment."
data input: "ADD"
data output: "ADD"
date: "2023-10-04"
output: html_document
---

>>>>

---
title: "Bias Analysis"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script combines quantifies bias in the data for plants and frugivores using various methods."
data input: "ADD"
data output: "ADD"
date: "2023-10-04"
output: html_document
---
